---
title: "class_1"
author: "Florencia D'Andrea"
date: "15/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## R Syntax Comparison 

> Extracted from [R Syntax Comparison Cheat Sheet](https://www.amelia.mn/blog/teaching/2018/02/11/Syntax-comparison.html) from Amelia McNamara

Syntax is the set of rules that govern what code works doesn’t work in a programming language. Most programming languages offer one standardized syntax, but R allows package developers to specify their own syntax. As a result, there is a large variety of (equally valid) R syntaxes. 

### Base R syntax

The **dollar sign syntax**, sometimes called base R syntax, expected by most base R functions. 

* It is characterized by the use of `dataset$variablename`
* Square bracket subsetting
`dataset[1,2]`.


```{r baser}

plot(x = diamonds$carat, #dollar sign operator
     y = diamonds$price)

```

### Tidyverse syntax

* These functions expect **data** to be the first argument, which allows them to work with the “pipe” (`%>%`) from the `magrittr` package

* Typically, `ggplot2` is thought of as part of the tidyverse, although it has its own flavor of the syntax using plus signs (`+`) to string pieces together. 

```{r ggplot2}

library(ggplot2) 

ggplot(data = diamonds, aes(x = carat, y = price)) + 
  geom_point()

```

## 
